Communication complexity: Chapter 3 \\ Distributional communication complexity

### 2019-04-14 CS860-CommunicationComplexity/assignments/Chapter3.tex
draft of fix for chapter 3

\begin{proof}
\replacethistext{Enter your proof here, if you complete it.}
\end{proof}

>>>>

\begin{proof}
Suppose $|A| > 2^{-\delta\sqrt{n}}{n\choose\sqrt{n}}.$ Let $M \in \R^{A\times B}$ be the matrix where
$$M_{S,T} = \Disj(S,T).$$
By the hypothesis of the proposition, at most $\alpha$ fraction of the entries of $M$ are such that $S\cap T \neq \emptyset$. We may assume without loss of generality that for every $S\in A$,
$$\Pr_{T \in B}[S\cap T \neq \emptyset] \leq 2\alpha.$$
If this assumption does not hold, we can remove the rows in $M$ for which this fails from $A$, reducing the size of $A$ by factor of at most $2$ (a factor we may compensate for in our choice of $\delta$).

Choose sets $S_1,\dots, S_{\sqrt{n}/3} \in A$ such that
$$|S_i\backslash (S_1\cup\dots\cup S_{i-1})| \geq \frac{\sqrt{n}}{2}$$
for all $i$. For small enough $\delta$, such $S_i$ exist by the lower bound on the size of $A$.

At least half of the sets $T \in B$ satisfy 
$$\Pr_{i \in [\sqrt{n}/3]}[ S_i\cap T \neq \emptyset] \leq 4\alpha,$$
since each row of $M$ has at most $2\alpha$ fraction of its entries $0$. But by our choice of $S_1,\dots, S_{\sqrt{n}/3}$ the number of such sets $T \in B$ is at most
$${\sqrt{n}/3\choose 4\alpha\sqrt{n}/3}{n-(1-4\alpha)n/6\choose \sqrt{n}}.$$
For $\delta>0$ small enough, this yields the desired bound on $|B|$.
\end{proof}
